---
title: "group"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(factoextra)
library(corrplot)
library(ggplot2)
library(data.table)
#install.packages("psych")
library(psych)

#install.packages("GPArotation")
library(GPArotation)
```

Input and View Data
```{r}
dataEda<-fread("bankdata_cleaned.csv")
view(dataEda)
```

## Job VS Deposit
## Job VS Balance

```{r pressure, echo=FALSE}
dataEda %>% 
  group_by(job) %>% 
  summarize(totalDeposit=sum(Deposit)) %>% 
  ggplot(aes(x=job,y=totalDeposit,fill=job)) +
  geom_col() + 
  labs(titles = "Jobs VS Deposit")

dataEda %>% 
  group_by(job) %>% 
  summarize(totalBalance=sum(balance)) %>% 
  ggplot(aes(x=job,y=totalBalance,fill=job)) +
  geom_col() + 
  labs(title="Jobs VS Balance")
```
## Age VS Deposit

```{r}

dataEda$ageRange<-findInterval(dataEda$age, c(10,20, 30, 40,50,60,70,80,90))

dataEda %>% 
  group_by(ageRange) %>% 
  summarize(totalDeposit=sum(Deposit)) %>% 
  ggplot(aes(x=ageRange,y=totalDeposit)) +
  geom_col()
```
## Education VS Deposit
```{r}
dataEda %>% 
  group_by(education) %>% 
  summarize(totalDeposit=sum(Deposit)) %>% 
  ggplot(aes(x=education,y=totalDeposit)) +
  geom_col()
```
## Duration VS Deposit
## Duration VS Balance
```{r}
range(dataEda$duration)
dataEda$DurationRange<-findInterval(dataEda$duration, c(0,1000,2000,3000))

dataEda %>% 
  group_by(DurationRange) %>% 
  summarize(totalDep=sum(Deposit)) %>% 
  ggplot(aes(x=DurationRange,y=totalDep)) +
  geom_col() + 
  labs(title = "Duration VS Deposit")

dataEda %>% 
  group_by(DurationRange) %>% 
  summarize(totalBal=sum(balance)) %>% 
  ggplot(aes(x=DurationRange,y=totalBal)) +
  geom_col() + 
  labs(title = "Duration VS Balance")
```
## Campain VS Deposit
## Campain VS Balance
```{r}
range(dataEda$campaign)
dataEda$CampRange<-findInterval(dataEda$campaign,c(0,5,10,15,20,25,30,35,40))

dataEda %>% 
  group_by(CampRange) %>% 
  summarize(totalDeposit=sum(Deposit)) %>% 
  ggplot(aes(x=CampRange,y=totalDeposit)) +
  geom_col() + 
  labs(title = "Campain VS Deposit")

dataEda %>% 
  group_by(CampRange) %>% 
  summarize(totalBal=sum(balance)) %>% 
  ggplot(aes(x=CampRange,y=totalBal)) +
  geom_col() + 
  labs(title = "Campain VS Balance")
```
## CampRange VS DurationgRange VS Deposit
```{r}
dataEda %>% 
  group_by(CampRange, DurationRange) %>% 
  summarize(totalDeposit=sum(Deposit)) %>% 
  ggplot(aes(x=CampRange,y=totalDeposit,fill=DurationRange)) +
  geom_col(position="dodge2") + 
  labs(title = "Campain VS Deposit")
```

# Results from EDA:
1. Most of the deposits are from the phone calls smaller than 2
2. Most of the deposits are from the duration smaller than 2000 secs
3. The people who has education level2 and 3 are most likely to deposit
4. People who has age from 30-50 are more likely to deposit, especially the people who are from 30-40, they have the highest rank to deposit
5. Depending on the job plots, it is very similar that the number of job who do the deposit and also the balance they deposti. 






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
